\documentclass[a4paper, 11pt]{report}
\input{config}

\begin{document}
    \input{titlepage}

    % Abstract
	{
		\FloatBarrier
		\newpage
        \setcounter{page}{2}
		\phantomsection
		\addcontentsline{toc}{chapter}{Abstract}
		\thispagestyle{plain}
		\vspace*{\fill}
			\section*{{\Large Abstract}}
			\input{chapters/abstract}
		\vspace*{\fill}
	}

    % Table of contents
    {
        \FloatBarrier
        \newpage
        \phantomsection
        \addcontentsline{toc}{chapter}{Contents}
        \tableofcontents
    }

    % Introduction: What is the problem?
	{
		\FloatBarrier
		\chapter{Introduction}
		\label{chp:introduction}
		\input{chapters/introduction}
	}

    % Solution: How to address this need?
	{
		\FloatBarrier
		\chapter{Solution: How to address this need?}
		\label{chp:solution}
		\input{chapters/solution}
	}

    % Technology: Why is it unique?
	{
		\FloatBarrier
		\chapter{Technology: Why is it unique?}
		\label{chp:technology}
		\input{chapters/technology}
	}

	% Business Model Canvas
	{
		\FloatBarrier
		\chapter{Business Model Canvas}
		\label{chp:business_model_canvas}
		\input{chapters/business_model_canvas}
	}

    % Business Model: How to capture value?
	{
		\FloatBarrier
		\chapter{Business Model: How to capture value?}
		\label{chp:business_model}
		\input{chapters/business_model}
	}

    % Strategic Analysis: What are the industry dynamics?
	{
		\FloatBarrier
		\chapter{Strategic Analysis: What are the industry dynamics?}
		\label{chp:strategic_analysis}
		\input{chapters/strategic_analysis}
	}

    % Marketing and sales: how will you sell it
	{
		\FloatBarrier
		\chapter{Marketing and sales: How to sell it?}
		\label{chp:marketing}
		\input{chapters/marketing}
	}

    % Competition: who else is in the game
	{
		\FloatBarrier
		\chapter{Competition: Who else is in the game?}
		\label{chp:competition}
		\input{chapters/competition}
	}

    % Implementation team: Who will implement the plan?
	{
		\FloatBarrier
		\chapter{Implementation team: Who will implement the plan?}
		\label{chp:implementation}
		\input{chapters/implementation}
	}

    % Status or timeline: Where are we now, what next?
	{
		\FloatBarrier
		\chapter{Status or timeline: Where are we now, what next?}
		\label{chp:timeline}
		\input{chapters/timeline}
	}

    % Executive summary: Concise overview of the opportunity
	{
		\FloatBarrier
		\chapter{Executive summary: Concise overview of the opportunity}
		\label{chp:summary}
		\input{chapters/summary}
	}

    % References
	{
		\FloatBarrier
		\newpage
		\phantomsection
		\addcontentsline{toc}{chapter}{References}
		\printbibliography[title = References]
	}

\end{document}
